---
title: "project_v2"
output: pdf_document
date: "2023-04-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#libraries
library(readxl)
library(ggplot2)
library(sjPlot)
library(lme4)
library(psych)
```

```{r}
data <- read_xlsx('./Data/taVNS.xlsx')
print(data)
```
```{r}
# Count the number of rows per ID
id_counts <- table(data$ID)

# Get the IDs with 96 rows
ids_to_keep <- names(id_counts[id_counts == 96])

# Subset the data
subset_data <- data[data$ID %in% ids_to_keep,]
data <- subset_data
print(data)
```

```{r}
# Assuming your dataset is called `data` and contains the variables `StimCond`, `Win`, `Food`, and `RewM`

# For Food
stim_0_win_food <- data$Win[data$StimCond == 0 & data$Food == 1]
stim_1_win_food <- data$Win[data$StimCond == 1 & data$Food == 1]

t_test_food <- t.test(stim_1_win_food, stim_0_win_food)
t_test_food
```

```{r}
# For RewM
stim_0_win_rewm <- data$Win[data$StimCond == 0 & data$Food == 0]
stim_1_win_rewm <- data$Win[data$StimCond == 1 & data$Food == 0]

t_test_rewm <- t.test(stim_1_win_rewm, stim_0_win_rewm)
t_test_rewm
```
```{r}
stim_0 <- data$Rating_want[data$StimCond == 0]
stim_1 <- data$Rating_want[data$StimCond == 1]

t_test_rewm <- t.test(stim_1, stim_0)
t_test_rewm
```

```{r}
# Assuming your dataset is called `data` and contains the variables `StimCond`, `Win`, `StimSide`

# For StimSide == 0
stim_0_win_0 <- data$Win[data$StimCond == 0 & data$StimSide == 0]
stim_1_win_0 <- data$Win[data$StimCond == 1 & data$StimSide == 0]

t_test_0 <- t.test(stim_1_win_0, stim_0_win_0)
t_test_0

# For StimSide == 1
stim_0_win_1 <- data$Win[data$StimCond == 0 & data$StimSide == 1]
stim_1_win_1 <- data$Win[data$StimCond == 1 & data$StimSide == 1]

t_test_1 <- t.test(stim_1_win_1, stim_0_win_1)
t_test_1
```

```{r}
# Assuming your dataset is called `data` and contains the variables `Diff`, `RewM`, and `S_InvSlope`

# Filter data by difficulty and rewm
data_75_0 <- data[data$Diff == 75.00 & data$RewM == 0, ]
data_75_1 <- data[data$Diff == 75.00 & data$RewM == 1, ]
data_85_0 <- data[data$Diff == 85.00 & data$RewM == 0, ]
data_85_1 <- data[data$Diff == 85.00 & data$RewM == 1, ]

# Calculate mean invigoration slope for each group
mean_slope_75_0 <- mean(data_75_0$S_InvSlope)
mean_slope_75_1 <- mean(data_75_1$S_InvSlope)
mean_slope_85_0 <- mean(data_85_0$S_InvSlope)
mean_slope_85_1 <- mean(data_85_1$S_InvSlope)

# Create bar plot
barplot(c(mean_slope_75_0, mean_slope_75_1, mean_slope_85_0, mean_slope_85_1),
        names.arg = c("75.00-0", "75.00-1", "85.00-0", "85.00-1"),
        xlab = "Difficulty-RewM",
        ylab = "Invigoration Slope",
        col = c("steelblue", "darkorange", "steelblue", "darkorange"),
        main = "Mean Invigoration Slope by Difficulty and RewM")


```

```{r}
# Assuming your dataset is called `data` and contains the variables `Diff`, `RewM`, and `RelFreq`

# Filter data by difficulty and rewm
data_75_0 <- data[data$Diff == 75.00 & data$RewM == 0, ]
data_75_1 <- data[data$Diff == 75.00 & data$RewM == 1, ]
data_85_0 <- data[data$Diff == 85.00 & data$RewM == 0, ]
data_85_1 <- data[data$Diff == 85.00 & data$RewM == 1, ]

# Calculate mean relative frequency for each group
mean_freq_75_0 <- mean(data_75_0$RelFreq)
mean_freq_75_1 <- mean(data_75_1$RelFreq)
mean_freq_85_0 <- mean(data_85_0$RelFreq)
mean_freq_85_1 <- mean(data_85_1$RelFreq)

# Create bar plot
barplot(c(mean_freq_75_0, mean_freq_75_1, mean_freq_85_0, mean_freq_85_1),
        names.arg = c("75.00-0", "75.00-1", "85.00-0", "85.00-1"),
        xlab = "Difficulty-RewM",
        ylab = "Relative Frequency",
        col =  c("forestgreen", "firebrick", "forestgreen", "firebrick"),
        main = "Mean Relative Frequency by Difficulty and RewM")

```

```{r}
# Assuming your dataset is called `data` and contains the variables `Diff`, `RewM`, and `S_InvSlope`

# Filter data by food and rewm
data_food_0 <- data[data$Food == 0 & data$RewM == 0, ]
data_food_1 <- data[data$Food == 1 & data$RewM == 0, ]
data_food_2 <- data[data$Food == 0 & data$RewM == 1, ]
data_food_3 <- data[data$Food == 1 & data$RewM == 1, ]

# Calculate mean invigoration slope for each group
mean_slope_food_0 <- mean(data_food_0$S_InvSlope)
mean_slope_food_1 <- mean(data_food_1$S_InvSlope)
mean_slope_food_2 <- mean(data_food_2$S_InvSlope)
mean_slope_food_3 <- mean(data_food_3$S_InvSlope)

# Create bar plot
barplot(c(mean_slope_food_0, mean_slope_food_1, mean_slope_food_2, mean_slope_food_3),
        names.arg = c("Food-0_RewM-0", "Food-1_RewM-0", "Food-0_RewM-1", "Food-1_RewM-1"),
        xlab = "Food-RewM",
        ylab = "Invigoration Slope",
        col = c("steelblue", "darkorange", "steelblue", "darkorange"),
        main = "Mean Invigoration Slope by Food and RewM")

```

```{r}
# Assuming your dataset is called `data` and contains the variables `Food`, `RewM`, and `RelFreq`

# Filter data by food and rewm
data_food_0 <- data[data$Food == 0 & data$RewM == 0, ]
data_food_1 <- data[data$Food == 1 & data$RewM == 0, ]
data_food_2 <- data[data$Food == 0 & data$RewM == 1, ]
data_food_3 <- data[data$Food == 1 & data$RewM == 1, ]

# Calculate mean relative frequency for each group
mean_freq_food_0 <- mean(data_food_0$RelFreq)
mean_freq_food_1 <- mean(data_food_1$RelFreq)
mean_freq_food_2 <- mean(data_food_2$RelFreq)
mean_freq_food_3 <- mean(data_food_3$RelFreq)

# Create bar plot
barplot(c(mean_freq_food_0, mean_freq_food_1, mean_freq_food_2, mean_freq_food_3),
        names.arg = c("Food-0_RewM-0", "Food-1_RewM-0", "Food-0_RewM-1", "Food-1_RewM-1"),
        xlab = "Food-RewM",
        ylab = "Relative Frequency",
        col =  c("forestgreen", "firebrick", "forestgreen", "firebrick"),
        main = "Mean Relative Frequency by Food and RewM")
```

```{r}
# Assuming your dataset is called `data` and contains the variables `S_InvSlope`, `Freq`, `Rating_exh`, and `Rating_want`

# Fit linear models to the data for each rating variable
lm_exh <- lm(Rating_exh ~ S_InvSlope + Freq, data = data)
lm_want <- lm(Rating_want ~ S_InvSlope + Freq, data = data)

# Extract the coefficients for each rating variable
coef_exh <- coef(lm_exh)[-1]
coef_want <- coef(lm_want)[-1]

# Define the colors for the plot
colors <- c("dodgerblue2", "firebrick")

# Create a bar plot of the coefficients for exertion ratings
barplot(coef_exh, col = colors[1], ylim = c(-1, 1),
        ylab = "Coefficient Value", main = "Regression Coefficients of Exertion Ratings",
        names.arg = c("Invigoration (S_InvSlope)", "Effort Maintenance (Freq)"))

# Create a bar plot of the coefficients for wanting ratings
barplot(coef_want, col = colors[2], ylim = c(-1, 1),
        ylab = "Coefficient Value", main = "Regression Coefficients of Wanting Ratings",
        names.arg = c("Invigoration (S_InvSlope)", "Effort Maintenance (Freq)"))

```
a Participants were quicker to invigorate if more reward was at stake, p < 0.001, and slower if difﬁculty was high, p = 0.002. 
b Participants exerted more effort when more reward was at stake, p < 0.001, and less when it became more difﬁcult to obtain it, p < 0.001. Moreover, they worked more for difﬁcult reward when the magnitude was high, p < 0.001. 
c Food and monetary rewards elicited comparable invigoration, p = 0.45. 
d Food and monetary rewards elicited similar investment of effort, p = 0.45.
```{r}
# Fit the mixed-effects model for stimcond = 0
model_stim0 <- lmer(Win ~ Freq + Work + S_InvSlope + Rating_exh + Rating_want + (1 | ID), data = subset(data, StimCond == 0))

# Check the summary of the model for stimcond = 0
summary(model_stim0)

# Plot the predicted values of win by stimcond = 0
plot_model(model_stim0, type = "pred", terms = c("Freq", "S_InvSlope"), axis.title = c("Frequency", "Invigoration"),
           show.values = TRUE, title = "Predicted values of win for StimCond = 0")
```

```{r}
# Fit the mixed-effects model for stimcond = 1
model_stim1 <- lmer(Win ~ RelFreq + Work + S_InvSlope + (1 | ID), data = subset(data, StimCond == 1))

# Check the summary of the model for stimcond = 1
summary(model_stim1)

# Plot the predicted values of win by stimcond = 1
plot_model(model_stim1, type = "pred", terms = c("RelFreq", "S_InvSlope"), axis.title = c("Frequency", "Invigoration"),
           show.values = TRUE, title = "Predicted values of win for StimCond = 1")
```

```{r}
# Fit the mixed-effects model for stimcond = 1
model <- lmer(Win ~ Freq + Work + S_InvSlope + Rating_exh + Rating_want + (1 | ID), data = data)

# Check the summary of the model for stimcond = 1
summary(model)

# Plot the predicted values of win by stimcond = 1
plot_model(model, type = "pred", terms = c("Freq", "S_InvSlope"), axis.title = c("Frequency", "Invigoration"),
           show.values = TRUE, title = "Predicted values of win")
```

```{r}

# filter the data for left and right ears
df_left <- subset(data, StimSide == 0)
df_right <- subset(data, StimSide == 1)

# create the four groups based on Food and StimCond variables for left ear
df_left_food_0 <- subset(df_left, Food == 0 & StimCond == 0)
df_left_money_0 <- subset(df_left, Food == 0 & StimCond == 1)
df_left_food_1 <- subset(df_left, Food == 1 & StimCond == 0)
df_left_money_1 <- subset(df_left, Food == 1 & StimCond == 1)

# create the four groups based on Food and StimCond variables for right ear
df_right_food_0 <- subset(df_right, Food == 0 & StimCond == 0)
df_right_money_0 <- subset(df_right, Food == 0 & StimCond == 1)
df_right_food_1 <- subset(df_right, Food == 1 & StimCond == 0)
df_right_money_1 <- subset(df_right, Food == 1 & StimCond == 1)

# calculate mean invigoration slope for each group for left ear
mean_inv_slope_left <- c(mean(df_left_food_0$S_InvSlope),
                         mean(df_left_money_0$S_InvSlope),
                         mean(df_left_food_1$S_InvSlope),
                         mean(df_left_money_1$S_InvSlope))

# calculate mean invigoration slope for each group for right ear
mean_inv_slope_right <- c(mean(df_right_food_0$S_InvSlope),
                          mean(df_right_money_0$S_InvSlope),
                          mean(df_right_food_1$S_InvSlope),
                          mean(df_right_money_1$S_InvSlope))

# create the bar plot for left and right ears
par(mfrow=c(1,2)) # set up the plot layout with 2 columns
barplot(mean_inv_slope_left, names.arg = c("Food_0","Money_0","Food_1", "Money_1"),
        ylab = "Mean Invigoration Slope", xlab = "Reward Type and Stimulation Condition",
        main = "Left Ear",col =  c("blue", "firebrick", "blue", "firebrick"))
barplot(mean_inv_slope_right, names.arg = c("Food_0","Money_0",  "Food_1", "Money_1"),
        ylab = "Mean Invigoration Slope", xlab = "Reward Type and Stimulation Condition",
        main = "Right Ear",col =  c("blue", "firebrick", "blue", "firebrick"))

# add a title for the entire plot
mtext("Mean Invigoration Slope by Reward Type and Stimulation Condition", side = 3, line = 2.5)
```

```{r}

# calculate Relative Frequency for each group for left ear
mean_freq_left <- c(mean(df_left_food_0$RelFreq),
                         mean(df_left_money_0$RelFreq),
                         mean(df_left_food_1$RelFreq),
                         mean(df_left_money_1$RelFreq))

# calculate Relative Frequency for each group for right ear
mean_freq_right <- c(mean(df_right_food_0$RelFreq),
                          mean(df_right_money_0$RelFreq),
                          mean(df_right_food_1$RelFreq),
                          mean(df_right_money_1$RelFreq))

# create the bar plot for left and right ears
par(mfrow=c(1,2)) # set up the plot layout with 2 columns
barplot(mean_freq_left, names.arg = c("Food_0","Money_0","Food_1", "Money_1"),
        ylab = "Relative Frequency", xlab = "Reward Type and Stimulation Condition",
        main = "Left Ear",col =  c("blue", "firebrick", "blue", "firebrick"))
barplot(mean_freq_right, names.arg = c("Food_0","Money_0",  "Food_1", "Money_1"),
        ylab = "Relative Frequency", xlab = "Reward Type and Stimulation Condition",
        main = "Right Ear",col =  c("blue", "firebrick", "blue", "firebrick"))

# add a title for the entire plot
mtext("Relative Frequency by Reward Type and Stimulation Condition", side = 3, line = 2.5)
```

```{r}
# Subset the data for stimcond=1
subset_data <- subset(data, StimCond == 1)

# Extract the Win values for left and right ear separately
Win_left <- subset_data$Win[subset_data$StimSide == "0"]
Win_right <- subset_data$Win[subset_data$StimSide == "1"]

# Compute the difference in Win between left and right ear stimulation
Win_diff <- Win_left - Win_right

# Perform a one-sided paired t-test with the null hypothesis that Win_left - Win_right <= 0
t.test(Win_diff, mu = 0, alternative = "greater", paired = FALSE)

```
```{r}
# Perform a one-sided paired t-test with the null hypothesis that Win_left - Win_right <= 0
t_test <- t.test(Win_diff, mu = 0, alternative = "greater", paired = FALSE)

# Correct for multiple comparisons using the FDR method
p_values <- t_test$p.value
p_adjusted <- p.adjust(p_values, method = "fdr")

# Print the adjusted p-values
p_adjusted

```

```{r}
subFood <- data[data$StimCond == 1 & data$Food == 1, ]

# Extract the Win values for left and right ear separately
Win_left <- subFood$Win[subFood$StimSide == "0"]
Win_right <- subFood$Win[subFood$StimSide == "1"]

# Compute the difference in Win between left and right ear stimulation
Win_diff <- Win_left - Win_right

# Perform a one-sided paired t-test with the null hypothesis that Win_left - Win_right <= 0
t.test(Win_diff, mu = 0, alternative = "greater", paired = FALSE)
```

```{r}
subMoney <- data[data$StimCond == 1 & data$Food == 0, ]

# Extract the Win values for left and right ear separately
Win_left <- subMoney$Win[subMoney$StimSide == "0"]
Win_right <- subMoney$Win[subMoney$StimSide == "1"]

# Compute the difference in Win between left and right ear stimulation
Win_diff <- Win_left - Win_right

# Perform a one-sided paired t-test with the null hypothesis that Win_left - Win_right <= 0
t.test(Win_diff, mu = 0, alternative = "greater", paired = FALSE)
```

```{r}
my_data$S_InvSlope <- as.numeric(my_data$S_InvSlope)
hist(data$S_InvSlope)
```

```{r}
# Perform ANOVA with S_InvSlope as the dependent variable
model_S_InvSlope <- aov(S_InvSlope ~ StimSide * StimCond * Diff * RewM * Food, data = data)

# Perform ANOVA with RelFreq as the dependent variable
model_RelFreq <- aov(RelFreq ~ StimSide * StimCond * Diff * RewM * Food, data = data)

# Print the ANOVA tables
summary(model_S_InvSlope)

summary(model_RelFreq)
```
```{r}
library(ggplot2)

# Extract the factor names and F values from the ANOVA table
anova_table <- summary(model_S_InvSlope)
factor_names <- rownames(anova_table[[1]])
f_values <- anova_table[[1]][, "F value"]

# Store the factor names and F values in a data frame
df_factors_fvalues <- data.frame(factor_names, f_values)

# Plot F-values
ggplot(df_factors_fvalues, aes(x = factor_names, y = f_values)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Factor", y = "F-value", title = "ANOVA F-values") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(colour = "gray90", size = 0.5)) +
  coord_flip()

```
```{r}
library(ggplot2)

# Extract the factor names and F values from the ANOVA table
anova_table <- summary(model_RelFreq)
factor_names <- rownames(anova_table[[1]])
f_values <- anova_table[[1]][, "F value"]

# Store the factor names and F values in a data frame
df_factors_fvalues <- data.frame(factor_names, f_values)

# Plot F-values
ggplot(df_factors_fvalues, aes(x = factor_names, y = f_values)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Factor", y = "F-value", title = "ANOVA F-values") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(colour = "gray90", size = 0.5)) +
  coord_flip()


```
```{r}
# Convert StimCond to a factor variable with levels 0 and 1
data$StimCond <- factor(data$StimCond, levels = c(0, 1))

# Perform ANOVA with S_InvSlope as the dependent variable
model_S_InvSlope <- aov(S_InvSlope ~ StimCond, data = data)

# Print the ANOVA table
summary(model_S_InvSlope)

# Perform Bonferroni post hoc test
posthoc_S_InvSlope <- TukeyHSD(model_S_InvSlope)

# View post hoc test results
posthoc_S_InvSlope


```

```{r}
# Convert StimCond to a factor variable with levels 0 and 1
data$StimCond <- factor(data$StimCond, levels = c(0, 1))

# Perform ANOVA with S_InvSlope as the dependent variable
model_RelFreq <- aov(RelFreq ~ StimCond, data = data)

# Print the ANOVA table
summary(model_RelFreq)

# Perform Bonferroni post hoc test
posthoc_RelFreq <- TukeyHSD(model_RelFreq)

# View post hoc test results
posthoc_RelFreq


```
```{r}
# Convert StimCond to a factor variable with levels 0 and 1
data$StimCond <- factor(data$StimCond, levels = c(0, 1))

# Perform ANOVA with S_InvSlope as the dependent variable
model_Work <- aov(Work ~ StimCond, data = data)

# Print the ANOVA table
summary(model_Work)

# Perform Bonferroni post hoc test
posthoc_Work <- TukeyHSD(model_Work)

# View post hoc test results
posthoc_Work


```



```{r}
# Load the necessary package
library(car)

# Fit the MANOVA model
model <- manova(cbind(S_InvSlope, RelFreq) ~ StimCond + StimSide + Food + Diff + RewM, data = data)

# Print the results
summary(model)

```

Mixed Effects Model
```{r}
data$StimCond <- as.factor(data$StimCond)
data$RewM <- as.factor(data$RewM)
data$Food <- as.factor(data$Food)
data$Diff <- as.factor(data$Diff)

# fit mixed-effects model
model <- lmer(S_InvSlope ~ StimCond + RewM + Food + Diff + (1 | ID), data = data)
summary(model)
```

Violin Plots
```{r}
# Load necessary libraries
library(ggplot2)

# Create a data frame with the variables of interest
df <- data.frame(
  StimCond = c(rep("0", 50), rep("1", 50)), # categorical predictor variable
  rating_exh = rnorm(100, mean = 5, sd = 1), # continuous response variable 1
  rating_want = rnorm(100, mean = 3, sd = 1) # continuous response variable 2
)

# Create the violin plot
ggplot(df, aes(x = StimCond, y = rating_exh, fill = StimCond)) +
  geom_violin(trim = FALSE) + # show full distribution
  geom_jitter(shape = 21, position = position_jitter(0.1)) + # add jittered points
  xlab("StimCond") +
  ylab("Rating Exh") +
  ggtitle("Distribution of Rating Exh by StimCond") +
  theme_minimal()

# Create the violin plot
ggplot(df, aes(x = StimCond, y = rating_want, fill = StimCond)) +
  geom_violin(trim = FALSE) + # show full distribution
  geom_jitter(shape = 21, position = position_jitter(0.1)) + # add jittered points
  xlab("StimCond") +
  ylab("Rating Want") +
  ggtitle("Distribution of Rating Want by StimCond") +
  theme_minimal()

```
Here, we start with a model that only includes the intercept (model1). Then we add each predictor variable one at a time, using anova() to compare the models to the previous one. The output of anova() tells us whether the added variable improved the model's performance (i.e., whether it's a significant predictor of S_InvSlope).
```{r}
library(lme4)

# Fit model with only intercept
model1 <- lmer(S_InvSlope ~ 1 + (1|ID), data = data)

# Add StimCond
model2 <- lmer(S_InvSlope ~ StimCond + (1|ID), data = data)
anova(model1, model2)

# Add RewM
model3 <- lmer(S_InvSlope ~ StimCond + RewM + (1|ID), data = data)
anova(model2, model3)

# Add Food
model4 <- lmer(S_InvSlope ~ StimCond + RewM + Food + (1|ID), data = data)
anova(model3, model4)

# Add Diff
model5 <- lmer(S_InvSlope ~ StimCond + RewM + Food + Diff + (1|ID), data = data)
anova(model4, model5)

```
The output shows the results of a hierarchical mixed-effects modeling analysis.

The first column indicates the models being compared, with the notation "model1" to "model5" representing increasingly complex models with additional predictor variables.

The second column shows the number of parameters (npar) estimated in each model.

The third and fourth columns display the Akaike information criterion (AIC) and Bayesian information criterion (BIC) values for each model, respectively. These criteria are used to compare the goodness of fit of different models, with lower values indicating a better fit.

The fifth column reports the log-likelihood of each model, which is the maximum value of the likelihood function for each model. Higher log-likelihood values indicate a better fit.

The sixth column shows the deviance, which is a measure of the goodness of fit of each model, with lower values indicating a better fit.

The seventh column displays the chi-squared (Chisq) test statistic for comparing the model being tested to the previous model in the hierarchy. A significant p-value indicates that the additional predictor variable(s) significantly improved the fit of the model.

The eighth column shows the degrees of freedom (Df) for the chi-squared test.

The final column reports the p-value for the chi-squared test, indicating the statistical significance of the improvement in fit due to the addition of the predictor variable(s).